Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-02 ms.tex
rest2
fixed compton accretion rate
challenges.

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then solving equation
(\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 150 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 130 \eta_{0.02}^{0.29}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate corresponding to the state where Compton heating limits the average accretion rate is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 1.3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.15}
&, \text{core}\\ 6\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
&, \text{cusp},
  \end{cases}
  \label{eq:MdotC}
\end{align}

@@

The cyclic model predicts that high $L_{X}$ nuclei should be more common in galaxies with younger stellar ages, a result which appears in tension with the finding by \citet{Pellegrini10} that galaxies with younger stellar populations are observed to host less X-ray luminous nuclei, at least for stellar ages $<3$ Gyr.  An alternative explanation for this observation within a thermally stable, steady-state accretion picture is that young stars provide higher stellar wind heating, reducing the mass accretion rate and hence nuclear X-ray luminosity.

@@

>>>>

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then solving equation
(\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 150 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 130 \eta_{0.02}^{0.29}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate corresponding to the state where Compton heating limits the average accretion rate is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 1.3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.15}
&, \text{core}\\ 6\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
&, \text{cusp},
  \end{cases}
  \label{eq:MdotCa}
\end{align}
If the accretion luminosity $\epsilon = \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}), then the Compton-limited accretion rate becomes
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 3\times 10^{-3} \eta_{0.02}^{0.11}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.08}
&, \text{core}\\ 2\times 10^{-3} \eta_{0.02}^{0.18}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}

@@

The cyclic model predicts that high $L_{X}$ nuclei should be more
common in galaxies with younger stellar ages, a result which appears
in tension with the finding by \citet{Pellegrini10} that galaxies with
younger stellar populations are observed to host less X-ray luminous
nuclei, at least for stellar ages $<3$ Gyr.  An alternative
explanation for this observation within a thermally stable,
steady-state accretion picture is that young stars provide higher
stellar wind heating, reducing the mass accretion rate and hence
nuclear X-ray luminosity.  {\bf AG Challenge: \citet{HeckmanBest:2014a}
  find that ${\rm L_{[OIII]}}$ (a proxy for the bolometric luminosity)
  ${\rm L_{[OIII]}/M_\star}$ (a proxy for the Eddington ratio)
  increases with decreasing 4000 $\AA$ break index (decreasing stellar
  age) (see their Figure 14). This suggests that the accretion rate is
  actually increasing towards younger stellar ages. At young ages
  there actually seems to be plenty of gas around, which may be
  obscuring the x-rays and causing an anamolously low measurement of
  $L_X$.

  For a starburst the black hole accretion rate lags the star
  formation rate by 200 Myr (\citet{WildHeckman+:2010a} Figure
  9). This could be due to SNe feed back suppressing the black hole
  accretion rate (massive star winds do the same thing by themselves,
  but they cannot be sustained for 200 Myr. 
}

@@

{\bf AG Challenge: Except in the most massive systems the jet duty
  cycle is rather low (0.001-0.01). The jets tend to overheat the gas,
  and then periodically turn once the gas begins to cools
  (Refs). Thus, jets cannot be treated as a truly steady source of
  heating. 
}
